Manuscript results: Forecasting influenza using ARIMA and ARIMAX

### 2025-06-23 manuscript_results.Rmd
uptade

------------
1 Week ahead
------------
```{r}

@@

head(df_W1_NoLg)
```

@@

head(df_W2_NoLg)
```

>>>>

```
------------
1 Week ahead
------------
```{r}

@@

head(df_W1_NoLg)
```
------------
2 Weeks ahead
-------------
```{r}
# Creating new columns with Epidemiological weeks based on target_end_week
AUTO_ARIMA_WEEK2$epiweek <- MMWRweek(AUTO_ARIMA_WEEK2$target_end_date)$MMWRweek
AUTO_ADJACENT_WEEK2$epiweek <- MMWRweek(AUTO_ADJACENT_WEEK2$target_end_date)$MMWRweek
AUTO_EPIWEEK_WEEK2$epiweek <- MMWRweek(AUTO_EPIWEEK_WEEK2$target_end_date)$MMWRweek
AUTO_TEMPERATURE_WEEK2$epiweek <- MMWRweek(AUTO_TEMPERATURE_WEEK2$target_end_date)$MMWRweek
AUTO_AVERAGE_WEEK2$epiweek <- MMWRweek(AUTO_AVERAGE_WEEK2$target_end_date)$MMWRweek

@@

head(df_W2_NoLg)
```
-------------
3 Weeks ahead
-------------
```{r}
# Creating new columns with Epidemiological weeks based on target_end_week
AUTO_ARIMA_WEEK3$epiweek <- MMWRweek(AUTO_ARIMA_WEEK3$target_end_date)$MMWRweek
AUTO_ADJACENT_WEEK3$epiweek <- MMWRweek(AUTO_ADJACENT_WEEK3$target_end_date)$MMWRweek
AUTO_EPIWEEK_WEEK3$epiweek <- MMWRweek(AUTO_EPIWEEK_WEEK3$target_end_date)$MMWRweek
AUTO_TEMPERATURE_WEEK3$epiweek <- MMWRweek(AUTO_TEMPERATURE_WEEK3$target_end_date)$MMWRweek
AUTO_AVERAGE_WEEK3$epiweek <- MMWRweek(AUTO_AVERAGE_WEEK3$target_end_date)$MMWRweek
